---
title: "R Notebook"
output: html_notebook
---


```{r}
# Required
install.packages("doParallel")
library(doParallel)

# Find how many cores are on your machine
detectCores() # Result = Typically 4 to 6

# Create Cluster with desired number of cores. Don't use them all! Your computer is running other processes. 
cl <- makeCluster(2)

# Register Cluster
registerDoParallel(cl)

# Confirm how many cores are now "assigned" to R and RStudio
getDoParWorkers() # Result 2 
```


```{r}
# create reproducable results from random sampling
set.seed(234)
```

```{r}
# Stop Cluster. After performing your tasks, stop your cluster. 
stopCluster(cl)
```

```{r}
install.packages("caret")
install.packages("plotly")
install.packages("dplyr")
install.packages("kknn")
install.packages("corrplot")
install.packages("corrr")
```

```{r}
library(caret)
library(plotly)
library(corrplot)
library(corrr)
library(dplyr)
```


```{r}
options(max.print=1000000)
options(scipen=999)
```

```{r}
largeMatrix <- read.csv("LargeMatrix.csv")
```


```{r}
# no nas present
sum(is.na(largeMatrix))
```

```{r}
iphone_smallMatrix <- read.csv("iphone_smallmatrix_labeled_8d.csv")
samsung_smallMatrix <- read.csv("galaxy_smallmatrix_labeled_9d.csv")
```

```{r}
# variables
names(iphone_smallMatrix)
names(samsung_smallMatrix)
```

```{r}
#summary
str(iphone_smallMatrix)
str(samsung_smallMatrix)

```

```{r}
# no missing values
sum(is.na(iphone_smallMatrix))
sum(is.na(samsung_smallMatrix))

```

```{r}
# There are no empty columns
colSums(iphone_smallMatrix)
colSums(samsung_smallMatrix)
```

```{r}
# visualize distribution of iphone and samsung sentiments
plot_ly(iphone_smallMatrix, x= ~iphone_smallMatrix$iphonesentiment, type='histogram')
plot_ly(samsung_smallMatrix, x= ~samsung_smallMatrix$galaxysentiment, type='histogram')
```

Notes:
0: very negative
1: negative
2: somewhat negative
3: somewhat positive
4: positive
5: very positive

Note to self:We already have too many innecessary predictors, including google, nokia, htc, and sony phones. We are only looking for samsung galaxy and iphone. 


```{r}
# correlation matrix
corr_matrixBIG <- cor(iphone_smallMatrix)
corr_plotBIG <- corrplot(as.matrix(corr_matrixBIG))
corr_plotBIG 
```


```{r}
# returns correlation  greater than .9
corr_df_big <- correlate(iphone_smallMatrix, diagonal = NA) %>% stretch()
# Examine variables with correlation above .9
corr_df_big_filtered <- corr_df_big %>% filter(r > .9)
```

Which variables will I keep? I copied corr_df_big_filtered into a spreadsheet and removed all duplicates.

googleperneg
googleperpos
htcdispos
htcphone
ios
iosperneg
iosperpos
iosperunc
iphone
nokiacamneg
nokiacampos
nokiacamunc
nokiadisneg
nokiadispos
nokiadisunc
nokiaperneg
nokiaperpos
nokiaperunc
samsungdisneg
samsungdispos
samsungdisunc
samsungperneg
samsungperunc

```{r}
#columns to remove

corr_to_remove <- c("googleperneg","googleperpos","htcdispos","htcphone","ios","iosperneg","iosperpos","iosperunc","iphone","nokiacamneg","nokiacampos","nokiacamunc","nokiadisneg","nokiadispos","nokiadisunc","nokiaperneg","nokiaperpos","nokiaperunc","samsungdisneg","samsungdispos","samsungdisunc","samsungperneg","samsungperunc")

# We may consider trying this, with keeping the iphone variable
```


```{r}
iphoneDFBigCOR <- iphone_smallMatrix[ , -which(names(iphone_smallMatrix) %in% corr_to_remove)]
```


```{r}
names(iphoneDFBigCOR)
```


# nzv

# Recursive Feature Elimination

```{r}
# Let's sample the data before using RFE
set.seed(123)
iphoneSample <- iphone_smallMatrix[sample(1:nrow(iphone_smallMatrix), 1000, replace=FALSE),]

# Set up rfeControl with randomforest, repeated cross validation and no updates
ctrl <- rfeControl(functions = rfFuncs, 
                   method = "repeatedcv",
                   repeats = 5,
                   verbose = FALSE)

# Use rfe and omit the response variable (attribute 59 iphonesentiment) 
rfeResultsBIG <- rfe(iphoneSample[,1:58], 
                  iphoneSample$iphonesentiment, 
                  sizes=(1:58), 
                  rfeControl=ctrl)

# Get results
rfeResultsBIG

# Plot results
plot(rfeResultsBIG, type=c("g", "o"))
```

BIG RFE
```{r}
# create new data set with rfe recommended features
iphoneDFBigRFE <- iphone_smallMatrix[,predictors(rfeResultsBIG)]

# add the dependent variable to iphoneRFE
iphoneDFBigRFE$iphonesentiment <- iphone_smallMatrix$iphonesentiment

# review outcome
str(iphoneDFBigRFE)
```


My_Data_Sets


iPhoneBig
 - iphoneDFBig <- iphone_smallMatrix
 - iphoneDFBigCOR <- 
 - iphoneDFBigNZV <- 
 - iphoneDFBigRFE <- iphoneDFBigRFE
 - iphoneDFBigRecoded <- optional tasks
 - iphoneDFBigPCA <- optional tasks


# Model Building

```{r}

# create 10-fold cross validation fitcontrol
fitControl <- trainControl(method = "cv", number = 10)
```


## iphoneDFBig

```{r}
# rename variables as necessary
iphoneDFBig <- iphone_smallMatrix
```


```{r}
# convert variable types, categorical
iphoneDFBig$iphonesentiment <- as.factor(iphoneDFBig$iphonesentiment)
```



Train and Test Set: 
```{r}
# Create Train and Test Set for iphoneDFBig
# create 75% sample of row indices
in_training <-createDataPartition(iphoneDFBig$iphonesentiment, p = .7, list = FALSE)
# create 75% sample of data and save it to trainData
trainData_iphoneDFBig <- iphoneDFBig[in_training, ]
 # create 25% sample of data and save it to test_data
testData_iphoneDFBig <- iphoneDFBig[-in_training, ]
# verify split percentages
nrow(trainData_iphoneDFBig) / nrow(iphoneDFBig)
```

```{r}
#c5
c5_iphoneDFBig <- train(iphonesentiment ~., data = trainData_iphoneDFBig, method = "C5.0",
                trControl = fitControl)
```


```{r}
# randomforest
rf_iphoneDFBig <- train(iphonesentiment ~., data = trainData_iphoneDFBig, method = "rf",
                trControl = fitControl)
```

```{r}
# svm   (kernlab)
svm_iphoneDFBig <- train(iphonesentiment ~., data = trainData_iphoneDFBig, method = "svmLinear",
                trControl = fitControl)
```


```{r}
# kknn
kknn_iphoneDFBig <- train(iphonesentiment ~., data = trainData_iphoneDFBig, method = "kknn",
                trControl = fitControl)
```

```{r}
# gbm
#gbm_iphoneDFBig <- train(iphonesentiment ~., data = trainData_iphoneDFBig, method = "gbm",
#                trControl = fitControl)
```

Compare Accuracy on Prediction Results:

```{r}
#c5
prediction_c5_iphoneDFBig <- predict(c5_iphoneDFBig, testData_iphoneDFBig)
postResample(prediction_c5_iphoneDFBig, testData_iphoneDFBig$iphonesentiment)
#randomforest
prediction_rf_iphoneDFBig  <- predict(rf_iphoneDFBig, testData_iphoneDFBig)
postResample(prediction_rf_iphoneDFBig, testData_iphoneDFBig$iphonesentiment)
#svm
prediction_svm_iphoneDFBig  <- predict(svm_iphoneDFBig, testData_iphoneDFBig)
postResample(prediction_svm_iphoneDFBig, testData_iphoneDFBig$iphonesentiment)
# kknn
prediction_kknn_iphoneDFBig  <- predict(kknn_iphoneDFBig, testData_iphoneDFBig)
postResample(prediction_kknn_iphoneDFBig, testData_iphoneDFBig$iphonesentiment)
# gbm
#prediction_gbm_iphoneDFBig  <- predict(gbm_iphoneDFBig, testData_iphoneDFBig)
#Model summary for comparisons
```
 Accuracy     Kappa 
0.7763496 0.5644448 
 Accuracy     Kappa 
0.7732648 0.5634731 
 Accuracy     Kappa 
0.7115681 0.4174966 
 Accuracy     Kappa 
0.3311054 0.1636461 
```{r}
modelData_iphoneDFBig <- resamples(list(C50 = c5_iphoneDFBig, randomForest = rf_iphoneDFBig, svMLinear = svm_iphoneDFBig,kknn = kknn_iphoneDFBig))
```

```{r}
summary(modelData_iphoneDFBig)
```

## iphoneDFBig


```{r}
# convert variable types, categorical
iphoneDFBigCOR$iphonesentiment <- as.factor(iphoneDFBigCOR$iphonesentiment)
```

Train and Test Set: 
```{r}
# Create Train and Test Set for iphoneDFBig
# create 75% sample of row indices
in_training <-createDataPartition(iphoneDFBig$iphonesentiment, p = .7, list = FALSE)
# create 75% sample of data and save it to trainData
trainData_iphoneDFBig <- iphoneDFBig[in_training, ]
 # create 25% sample of data and save it to test_data
testData_iphoneDFBig <- iphoneDFBig[-in_training, ]
# verify split percentages
nrow(trainData_iphoneDFBig) / nrow(iphoneDFBig)
```

```{r}
#c5
c5_iphoneDFBig <- train(iphonesentiment ~., data = trainData_iphoneDFBig, method = "C5.0",
                trControl = fitControl)
```


```{r}
# randomforest
rf_iphoneDFBig <- train(iphonesentiment ~., data = trainData_iphoneDFBig, method = "rf",
                trControl = fitControl)
```

```{r}
# svm   (kernlab)
svm_iphoneDFBig <- train(iphonesentiment ~., data = trainData_iphoneDFBig, method = "svmLinear",
                trControl = fitControl)
```


```{r}
# kknn
kknn_iphoneDFBig <- train(iphonesentiment ~., data = trainData_iphoneDFBig, method = "kknn",
                trControl = fitControl)
```

```{r}
# gbm
#gbm_iphoneDFBig <- train(iphonesentiment ~., data = trainData_iphoneDFBig, method = "gbm",
#                trControl = fitControl)
```

Compare Accuracy on Prediction Results:

```{r}
#c5
prediction_c5_iphoneDFBig <- predict(c5_iphoneDFBig, testData_iphoneDFBig)
postResample(prediction_c5_iphoneDFBig, testData_iphoneDFBig$iphonesentiment)
#randomforest
prediction_rf_iphoneDFBig  <- predict(rf_iphoneDFBig, testData_iphoneDFBig)
postResample(prediction_rf_iphoneDFBig, testData_iphoneDFBig$iphonesentiment)
#svm
prediction_svm_iphoneDFBig  <- predict(svm_iphoneDFBig, testData_iphoneDFBig)
postResample(prediction_svm_iphoneDFBig, testData_iphoneDFBig$iphonesentiment)
# kknn
prediction_kknn_iphoneDFBig  <- predict(kknn_iphoneDFBig, testData_iphoneDFBig)
postResample(prediction_kknn_iphoneDFBig, testData_iphoneDFBig$iphonesentiment)

```

```{r}
modelData_iphoneDFBig <- resamples(list(C50 = c5_iphoneDFBig, randomForest = rf_iphoneDFBig, svMLinear = svm_iphoneDFBig,kknn = kknn_iphoneDFBig))
```

```{r}
summary(modelData_iphoneDFBig)
```
## iphoneDFBigCOR

```{r}
# convert variable types, categorical
iphoneDFBigCOR$iphonesentiment <- as.factor(iphoneDFBigCOR$iphonesentiment)
```

Train and Test Set: 
```{r}
# Create Train and Test Set for iphoneDFBig
# create 75% sample of row indices
in_training <-createDataPartition(iphoneDFBig$iphonesentiment, p = .7, list = FALSE)
# create 75% sample of data and save it to trainData
trainData_iphoneDFBig <- iphoneDFBig[in_training, ]
 # create 25% sample of data and save it to test_data
testData_iphoneDFBig <- iphoneDFBig[-in_training, ]
# verify split percentages
nrow(trainData_iphoneDFBig) / nrow(iphoneDFBig)
```

```{r}
#c5
c5_iphoneDFBig <- train(iphonesentiment ~., data = trainData_iphoneDFBig, method = "C5.0",
                trControl = fitControl)
```


```{r}
# randomforest
rf_iphoneDFBig <- train(iphonesentiment ~., data = trainData_iphoneDFBig, method = "rf",
                trControl = fitControl)
```

```{r}
# svm   (kernlab)
svm_iphoneDFBig <- train(iphonesentiment ~., data = trainData_iphoneDFBig, method = "svmLinear",
                trControl = fitControl)
```


```{r}
# kknn
kknn_iphoneDFBig <- train(iphonesentiment ~., data = trainData_iphoneDFBig, method = "kknn",
                trControl = fitControl)
```

```{r}
# gbm
#gbm_iphoneDFBig <- train(iphonesentiment ~., data = trainData_iphoneDFBig, method = "gbm",
#                trControl = fitControl)
```

Compare Accuracy on Prediction Results:

```{r}
#c5
prediction_c5_iphoneDFBig <- predict(c5_iphoneDFBig, testData_iphoneDFBig)
postResample(prediction_c5_iphoneDFBig, testData_iphoneDFBig$iphonesentiment)
#randomforest
prediction_rf_iphoneDFBig  <- predict(rf_iphoneDFBig, testData_iphoneDFBig)
postResample(prediction_rf_iphoneDFBig, testData_iphoneDFBig$iphonesentiment)
#svm
prediction_svm_iphoneDFBig  <- predict(svm_iphoneDFBig, testData_iphoneDFBig)
postResample(prediction_svm_iphoneDFBig, testData_iphoneDFBig$iphonesentiment)
# kknn
prediction_kknn_iphoneDFBig  <- predict(kknn_iphoneDFBig, testData_iphoneDFBig)
postResample(prediction_kknn_iphoneDFBig, testData_iphoneDFBig$iphonesentiment)

```

```{r}
modelData_iphoneDFBig <- resamples(list(C50 = c5_iphoneDFBig, randomForest = rf_iphoneDFBig, svMLinear = svm_iphoneDFBig,kknn = kknn_iphoneDFBig))
```

```{r}
summary(modelData_iphoneDFBig)
```

## iphoneDFBigNZV
## iphoneDFBigRFE

## Choose final model: Evaluating model efficiency
```{r}
# Create a confusion matrix from random forest predictions 
cmC5 <- confusionMatrix(prediction_c5_iphoneDFBig, testData_iphoneDFBig$iphonesentiment) 
cmC5
cmRM <- confusionMatrix(prediction_rf_iphoneDFBig, testData_iphoneDFBig$iphonesentiment) 
cmRM
```


