---
title: "justIphone_variables"
output: html_notebook
---


```{r}
# keep only variables for iphones
toFilter <- grepl('iphone', colnames(iphone_smallMatrix))
 iphones <- iphone_smallMatrix[toFilter]
colnames(iphones)
```

# Correlation
```{r}
corr_matrix <- cor(iphones)
corr_plot <- corrplot(as.matrix(corr_matrix))
corr_plot
```

```{r}
# run this for any features that are h
any_over_80 <- function(my_matrix) any(my_matrix > .8 & my_matrix < 1, na.rm = TRUE)
any_under_80 <- function(my_matrix) any(my_matrix < -.8 & my_matrix > -1, na.rm = TRUE)
```

```{r}
# remove features with collinearity, correlation greater than .8, FOR small corr_matrix
corr_matrix %>% 
  focus_if(any_over_80, mirror = TRUE) 
```



Let's drop these variables: iphonedispos, iphonedisneg, iphonedisunc

Remove columns 5,6,7

Not all models are affected by collinearity
```{r}
# keep columns only for iphone and samsunggalaxy
iphones_corr <- iphones[,-(5:7)]
```


# NZR

```{r}
#nearZeroVar() with saveMetrics = TRUE returns an object containing a table including: frequency ratio, percentage unique, zero variance and near zero variance 

nzvMetrics <- nearZeroVar(iphones, saveMetrics = TRUE)
nzvMetrics
```


```{r}
# returns column 2, iphonecamunc, same as nvzMetrics
# nearZeroVar() with saveMetrics = FALSE returns an vector 
nzv <- nearZeroVar(iphones, saveMetrics = FALSE) 
nzv
```


```{r}
# create a new data set and remove near zero variance features
iphones_nvz <- iphones[,-nzv]
str(iphones_nvz)
```


visualize variable with nzv

```{r}
plot_ly(iphone_smallMatrix, x= ~iphone_smallMatrix$iphone, type='histogram')
plot_ly(iphone_smallMatrix, x= ~iphone_smallMatrix$iphonecampos, type='histogram')
plot_ly(iphone_smallMatrix, x= ~iphone_smallMatrix$iphonecamneg, type='histogram')
plot_ly(iphone_smallMatrix, x= ~iphone_smallMatrix$iphonecamunc, type='histogram')
plot_ly(iphone_smallMatrix, x= ~iphone_smallMatrix$iphonecamneg, type='histogram')
plot_ly(iphone_smallMatrix, x= ~iphone_smallMatrix$iphonedispos, type='histogram')
plot_ly(iphone_smallMatrix, x= ~iphone_smallMatrix$iphonedisneg, type='histogram')
plot_ly(iphone_smallMatrix, x= ~iphone_smallMatrix$iphonedisunc, type='histogram')
plot_ly(iphone_smallMatrix, x= ~iphone_smallMatrix$iphoneperpos, type='histogram')
plot_ly(iphone_smallMatrix, x= ~iphone_smallMatrix$iphoneperneg, type='histogram')
plot_ly(iphone_smallMatrix, x= ~iphone_smallMatrix$iphoneperunc, type='histogram')
plot_ly(iphone_smallMatrix, x= ~iphone_smallMatrix$iphonesentiment, type='histogram')
```

#rfe

```{r}
# Let's sample the data before using RFE
iphoneSample <- iphones[sample(1:nrow(iphones), 1000, replace=FALSE),]

# Set up rfeControl with randomforest, repeated cross validation and no updates
ctrl <- rfeControl(functions = rfFuncs, 
                   method = "repeatedcv",
                   repeats = 5,
                   verbose = FALSE)

# Use rfe and omit the response variable (attribute 11 iphonesentiment) 
rfeResultsSMALL <- rfe(iphoneSample[,1:10], 
                  iphoneSample$iphonesentiment, 
                  sizes=(1:10), 
                  rfeControl=ctrl)

# Get results
rfeResultsSMALL

# Plot results
plot(rfeResultsSMALL, type=c("g", "o"))
```


```{r}
# create new data set with rfe recommended features
iphones_RFE <- iphones[,predictors(rfeResultsSMALL)]

# add the dependent variable to iphoneRFE
iphones_RFE$iphonesentiment <- iphones$iphonesentiment

# review outcome
str(iphones_RFE)
```


# Model for Regular Data: Iphones

```{r}
# convert variable types, categorical
iphones$iphonesentiment <- as.factor(iphones$iphonesentiment)
```

Train and Test Set: 
```{r}
# Create Train and Test Set for iphoneDFBig
# create 75% sample of row indices
in_training <-createDataPartition(iphones$iphonesentiment, p = .7, list = FALSE)
# create 75% sample of data and save it to trainData
trainData_iphones <- iphones[in_training, ]
 # create 25% sample of data and save it to test_data
testData_iphones <- iphones[-in_training, ]
# verify split percentages
nrow(trainData_iphones) / nrow(iphones)
```

```{r}
#c5
c5_iphones <- train(iphonesentiment ~., data = trainData_iphones, method = "C5.0",
                trControl = fitControl)
```


```{r}
# randomforest
rf_iphones <- train(iphonesentiment ~., data = trainData_iphones, method = "rf",
                trControl = fitControl)
```

```{r}
# svm   (kernlab)
svm_iphones <- train(iphonesentiment ~., data = trainData_iphones, method = "svmLinear",
                trControl = fitControl)
```


```{r}
# kknn
kknn_iphones <- train(iphonesentiment ~., data = trainData_iphones, method = "kknn",
                trControl = fitControl)
```

```{r}
# gbm
#gbm_iphones <- train(iphonesentiment ~., data = trainData_iphones, method = "gbm",
#                trControl = fitControl)
```

Compare Accuracy on Prediction Results:

```{r}
#c5
prediction_c5_iphones <- predict(c5_iphones, testData_iphones)
postResample(prediction_c5_iphones, testData_iphones$iphonesentiment)
#randomforest
prediction_rf_iphones  <- predict(rf_iphones, testData_iphones)
postResample(prediction_rf_iphones, testData_iphones$iphonesentiment)
#svm
prediction_svm_iphones  <- predict(svm_iphones, testData_iphones)
postResample(prediction_svm_iphones, testData_iphones$iphonesentiment)
# kknn
prediction_kknn_iphones  <- predict(kknn_iphones, testData_iphones)
postResample(prediction_kknn_iphones, testData_iphones$iphonesentiment)

```

```{r}
modelData_iphones <- resamples(list(C50 = c5_iphones, randomForest = rf_iphones, svMLinear = svm_iphones,kknn = kknn_iphones))
```

```{r}
summary(modelData_iphones)
```

# Model for Correlated Data: 

```{r}
# convert variable types, categorical
iphones_corr$iphonesentiment <- as.factor(iphones_corr$iphonesentiment)
```

Train and Test Set: 
```{r}
# Create Train and Test Set for iphoneDFBig
# create 75% sample of row indices
in_training <-createDataPartition(iphones_corr$iphonesentiment, p = .7, list = FALSE)
# create 75% sample of data and save it to trainData
trainData_iphones_corr <- iphones_corr[in_training, ]
 # create 25% sample of data and save it to test_data
testData_iphones_corr <- iphones_corr[-in_training, ]
# verify split percentages
nrow(trainData_iphones_corr) / nrow(iphones_corr)
```

```{r}
#c5
c5_iphones_corr <- train(iphonesentiment ~., data = trainData_iphones_corr, method = "C5.0",
                trControl = fitControl)
```


```{r}
# randomforest
rf_iphones_corr <- train(iphonesentiment ~., data = trainData_iphones_corr, method = "rf",
                trControl = fitControl)
```

No:
```{r}
# svm   (kernlab)
svm_iphones_corr <- train(iphonesentiment ~., data = trainData_iphones_corr, method = "svmLinear",
                trControl = fitControl)
# kknn
kknn_iphones_corr <- train(iphonesentiment ~., data = trainData_iphones_corr, method = "kknn",
                trControl = fitControl)

# gbm
#gbm_iphones_corr <- train(iphonesentiment ~., data = trainData_iphones_corr, method = "gbm",
#                trControl = fitControl)
```

Compare Accuracy on Prediction Results:

```{r}
#c5
prediction_c5_iphones_corr <- predict(c5_iphones_corr, testData_iphones_corr)
postResample(prediction_c5_iphones_corr, testData_iphones_corr$iphonesentiment)
#randomforest
prediction_rf_iphones_corr  <- predict(rf_iphones_corr, testData_iphones_corr)
postResample(prediction_rf_iphones_corr, testData_iphones_corr$iphonesentiment)
```

No:
```{r}
#svm
prediction_svm_iphones_corr  <- predict(svm_iphones_corr, testData_iphones_corr)
postResample(prediction_svm_iphones_corr, testData_iphones_corr$iphonesentiment)
# kknn
prediction_kknn_iphones_corr  <- predict(kknn_iphones_corr, testData_iphones_corr)
postResample(prediction_kknn_iphones_corr, testData_iphones_corr$iphonesentiment)

```

```{r}
modelData_iphones_corr <- resamples(list(C50 = c5_iphones_corr, randomForest = rf_iphones_corr))
  
# svMLinear = svm_iphones_corr,kknn = kknn_iphones_corr))
```

```{r}
summary(modelData_iphones_corr)
```
# Model for NZR Data:


```{r}
# convert variable types, categorical
iphones_nvz$iphonesentiment <- as.factor(iphones_nvz$iphonesentiment)
```

Train and Test Set: 
```{r}
# Create Train and Test Set for iphoneDFBig
# create 75% sample of row indices
in_training <-createDataPartition(iphones_nvz$iphonesentiment, p = .7, list = FALSE)
# create 75% sample of data and save it to trainData
trainData_iphones_nvz <- iphones_nvz[in_training, ]
 # create 25% sample of data and save it to test_data
testData_iphones_nvz <- iphones_nvz[-in_training, ]
# verify split percentages
nrow(trainData_iphones_nvz) / nrow(iphones_nvz)
```

```{r}
#c5
c5_iphones_nvz <- train(iphonesentiment ~., data = trainData_iphones_nvz, method = "C5.0",
                trControl = fitControl)
```


```{r}
# randomforest
rf_iphones_nvz <- train(iphonesentiment ~., data = trainData_iphones_nvz, method = "rf",
                trControl = fitControl)
```

No:
```{r}
# svm   (kernlab)
svm_iphones_nvz <- train(iphonesentiment ~., data = trainData_iphones_nvz, method = "svmLinear",
                trControl = fitControl)
# kknn
kknn_iphones_nvz <- train(iphonesentiment ~., data = trainData_iphones_nvz, method = "kknn",
                trControl = fitControl)

# gbm
#gbm_iphones_nvz <- train(iphonesentiment ~., data = trainData_iphones_nvz, method = "gbm",
#                trControl = fitControl)
```

Compare Accuracy on Prediction Results:

```{r}
#c5
prediction_c5_iphones_nvz <- predict(c5_iphones_nvz, testData_iphones_nvz)
postResample(prediction_c5_iphones_nvz, testData_iphones_nvz$iphonesentiment)
#randomforest
prediction_rf_iphones_nvz  <- predict(rf_iphones_nvz, testData_iphones_nvz)
postResample(prediction_rf_iphones_nvz, testData_iphones_nvz$iphonesentiment)
```

No:
```{r}
#svm
prediction_svm_iphones_nvz  <- predict(svm_iphones_nvz, testData_iphones_nvz)
postResample(prediction_svm_iphones_nvz, testData_iphones_nvz$iphonesentiment)
# kknn
prediction_kknn_iphones_nvz  <- predict(kknn_iphones_nvz, testData_iphones_nvz)
postResample(prediction_kknn_iphones_nvz, testData_iphones_nvz$iphonesentiment)

```

```{r}
modelData_iphones_nvz <- resamples(list(C50 = c5_iphones_nvz, randomForest = rf_iphones_nvz))
  
# svMLinear = svm_iphones_nvz,kknn = kknn_iphones_nvz))
```

```{r}
summary(modelData_iphones_nvz)
```


# Models for RFE Data:



```{r}
# convert variable types, categorical
iphones_RFE$iphonesentiment <- as.factor(iphones_RFE$iphonesentiment)
```

Train and Test Set: 
```{r}
# Create Train and Test Set for iphoneDFBig
# create 75% sample of row indices
in_training <-createDataPartition(iphones_RFE$iphonesentiment, p = .7, list = FALSE)
# create 75% sample of data and save it to trainData
trainData_iphones_RFE <- iphones_RFE[in_training, ]
 # create 25% sample of data and save it to test_data
testData_iphones_RFE <- iphones_RFE[-in_training, ]
# verify split percentages
nrow(trainData_iphones_RFE) / nrow(iphones_RFE)
```

```{r}
#c5
c5_iphones_RFE <- train(iphonesentiment ~., data = trainData_iphones_RFE, method = "C5.0",
                trControl = fitControl)
```


```{r}
# randomforest
rf_iphones_RFE <- train(iphonesentiment ~., data = trainData_iphones_RFE, method = "rf",
                trControl = fitControl)
```

No:
```{r}
# svm   (kernlab)
svm_iphones_RFE <- train(iphonesentiment ~., data = trainData_iphones_RFE, method = "svmLinear",
                trControl = fitControl)
# kknn
kknn_iphones_RFE <- train(iphonesentiment ~., data = trainData_iphones_RFE, method = "kknn",
                trControl = fitControl)

# gbm
#gbm_iphones_RFE <- train(iphonesentiment ~., data = trainData_iphones_RFE, method = "gbm",
#                trControl = fitControl)
```

Compare Accuracy on Prediction Results:

```{r}
#c5
prediction_c5_iphones_RFE <- predict(c5_iphones_RFE, testData_iphones_RFE)
postResample(prediction_c5_iphones_RFE, testData_iphones_RFE$iphonesentiment)
#randomforest
prediction_rf_iphones_RFE  <- predict(rf_iphones_RFE, testData_iphones_RFE)
postResample(prediction_rf_iphones_RFE, testData_iphones_RFE$iphonesentiment)
```

No:
```{r}
#svm
prediction_svm_iphones_RFE  <- predict(svm_iphones_RFE, testData_iphones_RFE)
postResample(prediction_svm_iphones_RFE, testData_iphones_RFE$iphonesentiment)
# kknn
prediction_kknn_iphones_RFE  <- predict(kknn_iphones_RFE, testData_iphones_RFE)
postResample(prediction_kknn_iphones_RFE, testData_iphones_RFE$iphonesentiment)

```

```{r}
modelData_iphones_RFE <- resamples(list(C50 = c5_iphones_RFE, randomForest = rf_iphones_RFE))
  
# svMLinear = svm_iphones_RFE,kknn = kknn_iphones_RFE))
```

```{r}
summary(modelData_iphones_RFE)
```

