---
title: "task3_galaxy_cor"
output: html_notebook
---

```{r}
samsung <- read.csv("galaxy_smallmatrix_labeled_9d.csv")

```


# Correlation Matrix


```{r}
# correlation matrix
corr_matrix <- cor(samsung)
corr_plot <- corrplot(as.matrix(corr_matrix))
corr_plot
```


# Remove highly correlatedvariables
```{r}
# returns correlation  greater than .9
corr_df <- correlate(samsung, diagonal = NA) %>% stretch()
# Examine variables with correlation above .9
corr_df_filtered <- corr_df %>% filter(r > .9)
```

Which variables will I keep? I copied corr_df_big_filtered into a spreadsheet and removed all duplicates.

"iphone","htcphone","ios","nokiacampos","nokiacamneg","nokiacamunc","samsungdispos","sonydispos","nokiadispos","htcdispos","samsungdisneg","sonydisneg","nokiadisneg","samsungdisunc","nokiadisunc","nokiaperpos","samsungperneg","nokiaperneg","samsungperunc","nokiaperunc","iosperpos","googleperpos","iosperneg",

```{r}
#columns to remove

corr_to_remove <- c("iphone","htcphone","ios","nokiacampos","nokiacamneg","nokiacamunc","samsungdispos","sonydispos","nokiadispos","htcdispos","samsungdisneg","sonydisneg","nokiadisneg","samsungdisunc","nokiadisunc","nokiaperpos","samsungperneg","nokiaperneg","samsungperunc","nokiaperunc","iosperpos","googleperpos","iosperneg")

```


```{r}
samsungCOR <- samsung[ , -which(names(samsung) %in% corr_to_remove)]
```


```{r}
names(samsungCOR)
```



# Train Model

## Train and Test Set

```{r}
# convert variable types, categorical
samsungCOR$galaxysentiment <- as.factor(samsungCOR$galaxysentiment)
```

Train and Test Set: 
```{r}
# Create Train and Test Set for samsungCOR
# create 75% sample of row indices
in_training <-createDataPartition(samsungCOR$galaxysentiment, p = .7, list = FALSE)
# create 75% sample of data and save it to trainData
trainData_samsungCOR <- samsungCOR[in_training, ]
 # create 25% sample of data and save it to test_data
testData_samsungCOR <- samsungCOR[-in_training, ]
# verify split percentages
nrow(trainData_samsungCOR) / nrow(samsungCOR)
```


# Models
```{r}
#c5
c5_samsungCOR <- train(galaxysentiment ~., data = trainData_samsungCOR, method = "C5.0",
                trControl = fitControl)
```


```{r}
# randomforest
rf_samsungCOR <- train(galaxysentiment ~., data = trainData_samsungCOR, method = "rf",
                trControl = fitControl)
```

```{r}
## svm performed worst in out-of-box model test
# svm   (kernlab)
#svm_samsungCOR <- train(galaxysentiment ~., data = trainData_samsungCOR, method = "svmLinear",
#                trControl = fitControl)
```


```{r}
# kknn
kknn_samsungCOR <- train(galaxysentiment ~., data = trainData_samsungCOR, method = "kknn",
                trControl = fitControl)
```

```{r}
# gbm
#gbm_samsungCOR <- train(galaxysentiment ~., data = trainData_samsungCOR, method = "gbm",
#                trControl = fitControl)
```


# Model Summaries
Compare Accuracy on Prediction Results:

```{r}
#c5
prediction_c5_samsungCOR <- predict(c5_samsungCOR, testData_samsungCOR)
postResample(prediction_c5_samsungCOR, testData_samsungCOR$galaxysentiment)
#randomforest
prediction_rf_samsungCOR  <- predict(rf_samsungCOR, testData_samsungCOR)
postResample(prediction_rf_samsungCOR, testData_samsungCOR$galaxysentiment)
#svm
#prediction_svm_samsungCOR  <- predict(svm_samsungCOR, testData_samsungCOR)
#postResample(prediction_svm_samsungCOR, testData_samsungCOR$galaxysentiment)
# kknn
prediction_kknn_samsungCOR  <- predict(kknn_samsungCOR, testData_samsungCOR)
postResample(prediction_kknn_samsungCOR, testData_samsungCOR$galaxysentiment)

```

```{r}
modelData_samsungCOR <- resamples(list(C50 = c5_samsungCOR, randomForest = rf_samsungCOR, 
                                       #svMLinear = svm_samsungCOR,
                                       kknn = kknn_samsungCOR))
```

```{r}
summary(modelData_samsungCOR)
```
