---
title: "R Notebook"
output: html_notebook
---


```{r}
# Required
install.packages("doParallel")
library(doParallel)

# Find how many cores are on your machine
detectCores() # Result = Typically 4 to 6

# Create Cluster with desired number of cores. Don't use them all! Your computer is running other processes. 
cl <- makeCluster(2)

# Register Cluster
registerDoParallel(cl)

# Confirm how many cores are now "assigned" to R and RStudio
getDoParWorkers() # Result 2 
```


```{r}
# create reproducable results from random sampling
set.seed(234)
```

```{r}
# Stop Cluster. After performing your tasks, stop your cluster. 
stopCluster(cl)
```

```{r}
install.packages("caret")
install.packages("plotly")
install.packages("dplyr")
install.packages("kknn")
install.packages("corrplot")
install.packages("corrr")
```

```{r}
library(caret)
library(plotly)
library(corrplot)
library(corrr)
library(dplyr)
```


```{r}
options(max.print=1000000)
options(scipen=999)
```


```{r}
samsungDF <- read.csv("galaxy_smallmatrix_labeled_9d.csv")
```

```{r}
# variables
names(samsungDF)
```

```{r}
#summary
str(samsungDF)
```

```{r}
# no missing values
sum(is.na(samsungDF))

```

```{r}
# There are no empty columns
colSums(samsungDF)
```

```{r}
# visualize distribution of iphone and samsung sentiments
plot_ly(samsungDF, x= ~samsungDF$galaxysentiment, type='histogram')
```

Notes:
0: very negative
1: negative
2: somewhat negative
3: somewhat positive
4: positive
5: very positive




```{r}
# correlation matrix
corr_matrix <- cor(samsungDF)
corr_plot <- corrplot(as.matrix(corr_matrix))
corr_plot
```


```{r}
# returns correlation  greater than .9
corr_df <- correlate(samsungDF, diagonal = NA) %>% stretch()
# Examine variables with correlation above .9
corr_df_filtered <- corr_df %>% filter(r > .9)
```

Which variables will I keep? I copied corr_df_big_filtered into a spreadsheet and removed all duplicates.

"iphone","htcphone","ios","nokiacampos","nokiacamneg","nokiacamunc","samsungdispos","sonydispos","nokiadispos","htcdispos","samsungdisneg","sonydisneg","nokiadisneg","samsungdisunc","nokiadisunc","nokiaperpos","samsungperneg","nokiaperneg","samsungperunc","nokiaperunc","iosperpos","googleperpos","iosperneg",

```{r}
#columns to remove

corr_to_remove <- c("iphone","htcphone","ios","nokiacampos","nokiacamneg","nokiacamunc","samsungdispos","sonydispos","nokiadispos","htcdispos","samsungdisneg","sonydisneg","nokiadisneg","samsungdisunc","nokiadisunc","nokiaperpos","samsungperneg","nokiaperneg","samsungperunc","nokiaperunc","iosperpos","googleperpos","iosperneg")

```


```{r}
samsungCOR <- samsungDF[ , -which(names(samsungDF) %in% corr_to_remove)]
```


```{r}
names(samsungCOR)
```


# nzv

# Recursive Feature Elimination

```{r}
# Let's sample the data before using RFE
set.seed(123)
iphoneSample <- samsungDF[sample(1:nrow(samsungDF), 1000, replace=FALSE),]

# Set up rfeControl with randomforest, repeated cross validation and no updates
ctrl <- rfeControl(functions = rfFuncs, 
                   method = "repeatedcv",
                   repeats = 5,
                   verbose = FALSE)

# Use rfe and omit the response variable (attribute 59 galaxysentiment) 
rfeResultsBIG <- rfe(iphoneSample[,1:58], 
                  iphoneSample$galaxysentiment, 
                  sizes=(1:58), 
                  rfeControl=ctrl)

# Get results
rfeResultsBIG

# Plot results
plot(rfeResultsBIG, type=c("g", "o"))
```

BIG RFE
```{r}
# create new data set with rfe recommended features
samsungDFRFE <- samsungDF[,predictors(rfeResultsBIG)]

# add the dependent variable to iphoneRFE
samsungDFRFE$galaxysentiment <- samsungDF$galaxysentiment

# review outcome
str(samsungDFRFE)
```


My_Data_Sets


iPhoneBig
 - samsungDF <- samsungDF
 - samsungDFCOR <- 
 - samsungDFNZV <- 
 - samsungDFRFE <- samsungDFRFE
 - samsungDFRecoded <- optional tasks
 - samsungDFPCA <- optional tasks


# Model Building

```{r}

# create 10-fold cross validation fitcontrol
fitControl <- trainControl(method = "cv", number = 10)
```


## samsungDF


```{r}
# convert variable types, categorical
samsungDF$galaxysentiment <- as.factor(samsungDF$galaxysentiment)
```



Train and Test Set: 
```{r}
# Create Train and Test Set for samsungDF
# create 75% sample of row indices
in_training <-createDataPartition(samsungDF$galaxysentiment, p = .7, list = FALSE)
# create 75% sample of data and save it to trainData
trainData_samsungDF <- samsungDF[in_training, ]
 # create 25% sample of data and save it to test_data
testData_samsungDF <- samsungDF[-in_training, ]
# verify split percentages
nrow(trainData_samsungDF) / nrow(samsungDF)
```

```{r}
#c5
c5_samsungDF <- train(galaxysentiment ~., data = trainData_samsungDF, method = "C5.0",
                trControl = fitControl)
```


```{r}
# randomforest
rf_samsungDF <- train(galaxysentiment ~., data = trainData_samsungDF, method = "rf",
                trControl = fitControl)
```

```{r}
# svm   (kernlab)
svm_samsungDF <- train(galaxysentiment ~., data = trainData_samsungDF, method = "svmLinear",
                trControl = fitControl)
```


```{r}
# kknn
kknn_samsungDF <- train(galaxysentiment ~., data = trainData_samsungDF, method = "kknn",
                trControl = fitControl)
```

```{r}
# gbm
#gbm_samsungDF <- train(galaxysentiment ~., data = trainData_samsungDF, method = "gbm",
#                trControl = fitControl)
```

Compare Accuracy on Prediction Results:

```{r}
#c5
prediction_c5_samsungDF <- predict(c5_samsungDF, testData_samsungDF)
postResample(prediction_c5_samsungDF, testData_samsungDF$galaxysentiment)
#randomforest
prediction_rf_samsungDF  <- predict(rf_samsungDF, testData_samsungDF)
postResample(prediction_rf_samsungDF, testData_samsungDF$galaxysentiment)
#svm
prediction_svm_samsungDF  <- predict(svm_samsungDF, testData_samsungDF)
postResample(prediction_svm_samsungDF, testData_samsungDF$galaxysentiment)
# kknn
prediction_kknn_samsungDF  <- predict(kknn_samsungDF, testData_samsungDF)
postResample(prediction_kknn_samsungDF, testData_samsungDF$galaxysentiment)
# gbm
#prediction_gbm_samsungDF  <- predict(gbm_samsungDF, testData_samsungDF)
#Model summary for comparisons
```

```{r}
modelData_samsungDF <- resamples(list(C50 = c5_samsungDF, randomForest = rf_samsungDF, svMLinear = svm_samsungDF,kknn = kknn_samsungDF))
```

```{r}
summary(modelData_samsungDF)
```


Train and Test Set: 
```{r}
# Create Train and Test Set for samsungDF
# create 75% sample of row indices
in_training <-createDataPartition(samsungDF$galaxysentiment, p = .7, list = FALSE)
# create 75% sample of data and save it to trainData
trainData_samsungDF <- samsungDF[in_training, ]
 # create 25% sample of data and save it to test_data
testData_samsungDF <- samsungDF[-in_training, ]
# verify split percentages
nrow(trainData_samsungDF) / nrow(samsungDF)
```

```{r}
#c5
c5_samsungDF <- train(galaxysentiment ~., data = trainData_samsungDF, method = "C5.0",
                trControl = fitControl)
```


```{r}
# randomforest
rf_samsungDF <- train(galaxysentiment ~., data = trainData_samsungDF, method = "rf",
                trControl = fitControl)
```

```{r}
# svm   (kernlab)
svm_samsungDF <- train(galaxysentiment ~., data = trainData_samsungDF, method = "svmLinear",
                trControl = fitControl)
```


```{r}
# kknn
kknn_samsungDF <- train(galaxysentiment ~., data = trainData_samsungDF, method = "kknn",
                trControl = fitControl)
```

```{r}
# gbm
#gbm_samsungDF <- train(galaxysentiment ~., data = trainData_samsungDF, method = "gbm",
#                trControl = fitControl)
```

Compare Accuracy on Prediction Results:

```{r}
#c5
prediction_c5_samsungDF <- predict(c5_samsungDF, testData_samsungDF)
postResample(prediction_c5_samsungDF, testData_samsungDF$galaxysentiment)
#randomforest
prediction_rf_samsungDF  <- predict(rf_samsungDF, testData_samsungDF)
postResample(prediction_rf_samsungDF, testData_samsungDF$galaxysentiment)
#svm
prediction_svm_samsungDF  <- predict(svm_samsungDF, testData_samsungDF)
postResample(prediction_svm_samsungDF, testData_samsungDF$galaxysentiment)
# kknn
prediction_kknn_samsungDF  <- predict(kknn_samsungDF, testData_samsungDF)
postResample(prediction_kknn_samsungDF, testData_samsungDF$galaxysentiment)

```

```{r}
modelData_samsungDF <- resamples(list(C50 = c5_samsungDF, randomForest = rf_samsungDF, svMLinear = svm_samsungDF,kknn = kknn_samsungDF))
```

```{r}
summary(modelData_samsungDF)
```


## Choose final model: Evaluating model efficiency
```{r}
# Create a confusion matrix from random forest predictions 
cmC5 <- confusionMatrix(prediction_c5_samsungDF, testData_samsungDF$galaxysentiment) 
cmC5
cmRM <- confusionMatrix(prediction_rf_samsungDF, testData_samsungDF$galaxysentiment) 
cmRM
```



